Money management skills are vital life skills, especially for young people, because wealth development is not solely based on an individual's capacity to work hard, but also on aspects such as his or her ability to grasp how money works and implement its management principles. Savings are the backbone of personal financial success, so they are an important part of a person's financial management abilities. Savings entails not just putting money away for future use, but also keeping anything of economic worth. That is to say, saving creates security reassurance for the unknowns of the future.\cite{Loibl}

Savings habits play a significant role in daily financial decisions. Research has shown that there is an increasing association between savings and growth. Saving on a regular basis is critical for financial independence and security. Greater savings has been proven to be an important component of fiscal development. To attain personal financial independence in an era of uncertain financial economies, one must ensure and implement smart financial management techniques, of which savings are critically important. As the world is predominantly plagued by ever-increasing rates of unemployment, savings have become vital in the lives of college students who aspire to acquire personal financial independence.\cite{Fiergbor} As the market continues to evolve with new consumer products, financial literacy in the area of saving is essential.

Even though habit creation is a difficult task, when establishing a saving habit, it can enhance a person's perception and intention to save. When a habit is fully developed, it can also have an positive impact on a person's consumption and savings. Savings is based on one's previous savings as well as a combination of current income changes and the "discounted value of future income changes." The habit of saving is, therefore, extremely important. As optimal financial leverage not only promotes a sound and stable economic life, but it is also critical in ensuring and assuring a better lifestyle in areas such as healthy living, quality health care, education, and better access to basic social amenities.\cite{Alessie} Savings is an important element of life because it is required in almost every aspect of life, and the ability to develop the habit will help you achieve financial success.